### 2019-01-08 Sections/protocols_for_the_quantum_internet.tex
Open dest QST figs

In the standard quantum state teleportation protocol there is a single sender and a single receiver. A generalisation of the protocol is \textit{open-destination quantum state teleportation}, whereby there is still just one sender, but any number of potential recipients. At the time of transmission, the sender does not specify the recipient, but rather wishes to `broadcast' the state to \textit{all} recipients, such that any \textit{one} of them can subsequently read out the state. Note that only a single recipient may actually perform the readout, since multiple readouts would violate the no-cloning theorem\index{No-cloning theorem}. However, the key new feature introduced by this variant of the protocol is that the final choice of which recipient performs the readout needn't be known in advance, but can be decided at an arbitrary later stage, well after the sender has completed their side of the protocol.

@@

The full protocol is described in Alg.~\ref{alg:open_dest_qst}. This protocol was successfully experimentally demonstrated photonically using 5 qubits \cite{bib:PanOpenDest}, with high teleported state fidelities.

\begin{table}[!htbp]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function OpenDestTeleportation($\ket\phi_A$, $\ket{\psi_\mathrm{GHZ}^{(n)}}$):
\begin{enumerate}
    \item An $n$-qubit GHZ state is distributed between the sender and \mbox{$n-1$} potential recipients,
    \begin{align}
    	\ket{\psi_\mathrm{GHZ}^{(n)}} = \frac{1}{\sqrt{2}}(\ket{0}^{\otimes n} + \ket{1}^{\otimes n}).
    \end{align}
    \item The sender completes their side of the protocol as per the ordinary 2-party quantum state teleportation protocol.
    \item The sender's classical measurement outcome is broadcast to all potential recipients.
    \item Wait until the potential recipients have decided between themselves (classically) who shall be the recipient.
    \item All non-recipients measure their qubits in the $\hat{X}$-basis and publicly announce their measurement outcomes.
    \item The recipient calculates the parity of the announced measurement outcomes, which determines whether they apply a local $\hat{Z}$-correction.
    \item The recipient completes their side of the protocol as per the usual quantum state teleportation protocol, obtaining $\ket\phi$.
    \item $\Box$
\end{enumerate}}
\end{mdframed}
\captionspacealg \caption{Open-destination quantum state teleportation of a single qubit from a single sender to \mbox{$n-1$} potential recipients.} \label{alg:open_dest_qst}
\end{table}

>>>>

In the standard quantum state teleportation protocol there is a single sender and a single receiver. A generalisation of the protocol is \textit{open-destination quantum state teleportation}, whereby there is still just one sender, but any number of potential recipients. At the time of transmission, the sender does not specify the recipient, but rather wishes to `broadcast'\index{Broadcasting} the state to \textit{all} recipients, such that any \textit{one} of them can subsequently read out the state. Note that only a single recipient may actually perform the readout, since multiple readouts would violate the no-cloning theorem\index{No-cloning theorem}. However, the key new feature introduced by this variant of the protocol is that the final choice of which recipient performs the readout needn't be known in advance, but can be decided at an arbitrary later stage, well after the sender has completed their side of the protocol.

@@

The full protocol is described in Alg.~\ref{alg:open_dest_qst}, and outlined in Fig.~\ref{fig:open_dest_teleport}. This protocol was successfully experimentally demonstrated photonically using 5 qubits \cite{bib:PanOpenDest}, with high teleported state fidelities.

\begin{table}[!htbp]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function OpenDestTeleportation($\ket\phi_A$, $\ket{\psi_\mathrm{GHZ}^{(n)}}$):
\begin{enumerate}
    \item An $n$-qubit GHZ state is distributed between the sender and \mbox{$n-1$} potential recipients,
    \begin{align}
    	\ket{\psi_\mathrm{GHZ}^{(n)}} = \frac{1}{\sqrt{2}}(\ket{0}^{\otimes n} + \ket{1}^{\otimes n}).
    \end{align}
    \item The sender completes their side of the protocol as per the ordinary 2-party quantum state teleportation protocol.
    \item The sender's classical measurement outcome is broadcast to all potential recipients.
    \item Wait until the potential recipients have decided between themselves (classically) who shall be the recipient.
    \item All non-recipients measure their qubits in the $\hat{X}$-basis and publicly announce their measurement outcomes.
    \item The recipient calculates the parity of the announced measurement outcomes, which determines whether they apply a local $\hat{Z}$-correction.
    \item The recipient completes their side of the protocol as per the usual quantum state teleportation protocol, obtaining $\ket\phi$.
    \item $\Box$
\end{enumerate}}
\end{mdframed}
\captionspacealg \caption{Open-destination quantum state teleportation of a single qubit from a single sender to \mbox{$n-1$} potential recipients.}\index{Open-destination quantum state teleportation}\label{alg:open_dest_qst}
\end{table}

\if 2\pubmode
	\begin{figure}[!htbp]
	\includegraphics[clip=true, width=0.475\textwidth]{open_dest_teleport_long}
	\captionspacefig \caption{Open-destination quantum state teleportation. (a) GHZ state distribution from a central server between the sender and all potential recipients. (b) Sender performs quantum state teleportation. (c) All non-receivers measure out their qubits in the $\hat{X}$-basis, resulting in the teleported state arriving at the destination of the chosen true receiver.}\index{Open-destination quantum state teleportation}\label{fig:open_dest_teleport}
	\end{figure}
\else
	\begin{figure*}[!htbp]
	\includegraphics[clip=true, width=\textwidth]{open_dest_teleport}
	\captionspacefig \caption{Open-destination quantum state teleportation. (a) GHZ state distribution from a central server between the sender and all potential recipients. (b) Sender performs quantum state teleportation. (c) All non-receivers measure out their qubits in the $\hat{X}$-basis, resulting in the teleported state arriving at the destination of the chosen true receiver.}\index{Open-destination quantum state teleportation}\label{fig:open_dest_teleport}
	\end{figure*}
\fi
